Modelling the City of Melbourne Pedestrian Data

### 2017-10-01 presentation/final.Rmd
fixed plot on slide 21

```{r, echo = FALSE, fig.retina = 6, message=FALSE, warning=F, fig.width = 3.5, fig.height = 3.5}
ggplot(test_df, aes(x = `Bourke Street Mall (North)`,
                    y = test_fit$`Bourke Street Mall (North)`)) +
                  geom_point(alpha = 0.5) +
                  scale_x_continuous(limits = c(0, 5000)) +
                  scale_y_continuous(limits = c(0, 5000)) +
                  xlab("Actual") + ylab("Fitted") + theme(aspect.ratio = 1) +
                  geom_abline(aes(slope = 1, intercept = 0),
                              colour = viridis(3)[1],
                              alpha = 0.7, size = 1.5,
                              linetype = 2) +
                  geom_smooth(method = "lm", size = 1.5, 
                       colour = viridis(3)[3]) +
                  ggtitle("Actual vs Fitted \n at Bourke Street Mall (North) in 2017")

>>>>

```{r, echo = FALSE, fig.retina = 6, message=FALSE, warning=F, fig.width = 4.5, fig.height = 3.5}
ggplot(test_df, aes(x = `Bourke Street Mall (North)`,
                    y = test_fit$`Bourke Street Mall (North)`)) +
                  geom_point(alpha = 0.5) +
                  scale_x_continuous(limits = c(0, 5000)) +
                  scale_y_continuous(limits = c(0, 5000)) +
                  xlab("Actual") + ylab("Fitted") + theme(aspect.ratio = 1) +
                  geom_abline(aes(slope = 1, intercept = 0),
                              colour = viridis(3)[1],
                              alpha = 0.7, size = 1.5,
                              linetype = 2) +
                  geom_smooth(method = "lm", size = 1.5, 
                       colour = viridis(3)[3]) +
                  ggtitle("Actual vs Fitted \n at Bourke Street Mall (North) in 2017")
